%-------------------------
% Resume in Latex
% Author : Ada Lyons
% Based on: Sourabh Bajaj repo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \underline{#1:} #2
}

% COLOR THEMES SELECTION

% For Light theme un-comment this and comment the Dark theme section below
\colorlet{textcolor}{black}
\colorlet{urlcolor}{blue}

\begin{document}
% ---

% For Dark theme un-comment this and comment the Light theme section above
% \colorlet{textcolor}{white!80!gray}
% \colorlet{backgroundcolor}{black!30!gray}
% \colorlet{urlcolor}{blue!25!white}
% \AtBeginDocument{\color{textcolor}}
% \newcommand{\otherThemeRef}{\href{https://github.com/slyons/resume/raw/master/scott_lyons_light.pdf}{Light \color{urlcolor}{\faicon{lightbulb-o}}}}
% \newcommand{\latestVersion}{\href{https://github.com/slyons/resume/raw/master/scott_lyons_dark.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

% \begin{document}
% \pagecolor{backgroundcolor}
% ---

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ada Lyons} \\
  Senior Engineer & \href{mailto:ada.g.lyons@gmail.com}{\color{urlcolor}{\faicon{envelope}} \color{textcolor} ada.g.lyons@gmail.com} \\
  \textsl{Seattle, Washington} & \href{https://www.linkedin.com/in/eadgbear/}{ \color{urlcolor}{\faicon{linkedin}} \color{textcolor} eadgbear} \\
  %\textsl{\small \latestVersion} /\textsl{\small \otherThemeRef} & \href{https://github.com/eadgbear}{  \color{urlcolor}{\faicon{github}} \color{textcolor} eadgbear}\\
   & \href{https://github.com/eadgbear}{  \color{urlcolor}{\faicon{github}} \color{textcolor} eadgbear}\\
\end{tabular*}
% ---

\section{Professional Summary}
Senior Engineer with more than a decade of experience designing and building scalable data infrastructure, leading cross-functional engineering efforts, and mentoring teams in high-impact projects. Deep expertise in modern data processing frameworks such as Apache DataFusion, Spark, and Databricks, with a strong foundation in Rust, Python, and cloud-native architectures. Proven track record in translating complex business requirements into robust, performant systems in start-up and enterprise environments.

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Embucket}{Remote}
      {Senior Engineer}{January 2025 - Current}
      \resumeItemListStart
      \resumeItem{Scoped and planned the development of a DataFusion-based product, ensuring alignment with business objectives and technical feasibility.}
      \resumeItem{Provided technical leadership by contributing to core components of the product, including query optimization and execution planning.}
      \resumeItem{Mentored team members unfamiliar with Rust, offering workshops, code reviews, and pair programming sessions to accelerate their learning curve.}
      \resumeItem{Guided the team in understanding and leveraging Apache DataFusion's architecture and APIs for building scalable data processing solutions.}
      \resumeItem{Collaborated with stakeholders to define clear deliverables and timelines, ensuring the project stayed on track and met quality standards.}
      \resumeItem{Fostered a collaborative environment by encouraging knowledge sharing and establishing best practices for Rust and DataFusion development.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Rust, Apache DataFusion, AWS, Kubernetes, Terraform, Docker, Python, Apache Iceberg, Snowflake}\\

      \resumeSubheading
      {Spice.ai}{Seattle, Washington (Remote)}
      {Senior Engineer}{September 2024 - November 2024}
      \resumeItemListStart
      \resumeItem{Enhanced the open-source Spice.ai product, focusing on core data pipeline optimizations.}
      \resumeItem{Implemented new key features and optimizations in the Spice.ai product, improving performance and usability.}
      \resumeItem{Authored API references and deployment guides to streamline the integration of Spice.ai into existing data systems.}
      \resumeItem{Produced instructional content to educate developers on deploying and using data-intensive applications.}
      \resumeItem{Utilized core design principles to guide content creation, ensuring that all resources provide actionable insights and adhere to Spice.ai's strategic goals and technical standards}
      \resumeItemListEnd
      \resumeTech{Technologies}{Rust, Apache DataFusion, Spark, AWS, Azure, Axum, Kubernetes, Data Catalogs, DuckDB}\\

    \resumeSubheading
      {Prophecy.io}{Seattle, Washington (Remote)}
      {Staff Data Engineer}{April 2022 - September 2024}
      \resumeItemListStart
      \resumeItem{Designed and developed modern data pipelines for enterprise-scale big data ecosystems.}
      \resumeItem{Built reusable, production-grade components to accelerate data pipeline development.}
      \resumeItem{Migrated complex legacy ETL systems to robust, modern architectures using tools like Databricks, S3 and Azure Data Lake.}
      \resumeItem{Established best practices for Data Engineering workflows with customers, integrating CI/CD for data infrastructure.}
      \resumeItem{Worked with customers to migrate existing legacy ETL projects to more modern Big Data ecosystems}
      \resumeItem{Created best Data Engineering practice guidelines both internally and with customers}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, SQL, Databricks, Scala, Spark, Terraform, Azure Data Factory, Azure Data Lake, Kubernetes, Data Catalogs}\\

    \newpage

    \resumeSubheading
      {Microsoft - Consumer Software Engineering (CSE)}{Redmond, Washington}
      {Software Engineer 2}{September 2018 - April 2022}
      \resumeItemListStart
      \resumeItem{Member of the Data Tech Domain team gathering industry trends from various Customer engagements and projects}
      \resumeItem{Responsible for educating customers and field-oriented developers on industry trends related to Big Data.}
      \resumeItem{Collected feedback from field teams, triaged it and reported it back to Product groups}
      \resumeItem{Worked closely as part of the Azure Databricks feedback loop to expedite customer issues and drive product planning based on industry trends}
      \resumeItem{Designed Data Architecture and built the initial Spark Streaming version of near-realtime ML models (Energinet)}
      \resumeItem{Wrote benchmarking tests dealing with handling encrypted files in a Big Data pipeline (Walgreens)}
      \resumeItem{Wrote initial Spark/HBase implementation for distributed event handling through Event Grid (AT\&T)}
      \resumeItem{Served as an emergency consultant on scripting and validating HDInsight cluster deployments (Credit Suisse)}
      \resumeItem{Helped port \href{https://github.com/feast-dev/feast}{Feast}(https://github.com/feast-dev/feast) to run on Azure Databricks}
      \resumeItem{Did design reviews for large-scale data warehousing scenarios (Kroger)}
      \resumeItem{Built the infrastructure deployment automation for the CSE Kafka on-boarding event using Terraform and Kafka}
      \resumeItem{Wrote benchmarking tools to test CosmosDB's Cassandra offering}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, SQL, Azure Databricks, Scala, Spark, Terraform, Docker, Cassandra, Kubernetes, Azure Data Factory, EventHubs, Kafka, Azure Data Lake, Azure HDInsight, Azure CosmosDB}\\
      
    \sepsection

    \resumeSubheading
      {Microsoft - Customer Advisory Team (CAT/DataCAT)}{Redmond, Washington}
      {Software Engineer 2}{September 2015 - August 2018}
      \resumeItemListStart
      \resumeItem{Modernized legacy SQL pipelines by transitioning to Spark/Hadoop, achieving significant cost and performance benefits.}
      \resumeItem{Led design reviews for customer ETL and OLTP workflows, optimizing architectures for scale and efficiency.}
      \resumeItem{Lead a team to convert a legacy SQL pipeline to Spark/Hadoop, reducing hardware cost by 80\% and runtime by 96\% }
      \resumeItem{Helped plan an internal project that lead to key design decisions in ADLS Gen 2 (Hierarchical Namespaces)}
      \resumeItem{Delivered GDPR-compliant IoT streaming architectures with Spark, EventHubs, and Akka.}
      \resumeItem{Partnered with product teams to enhance EventHubs Spark driver performance, enabling higher throughput data processing.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, SQL, Scala, Azure Databricks, Hadoop, Yarn, Azure HDInsight, Azure CosmosDB, Kubernetes, EventHubs, Airflow, MongoDB.}\\

    \resumeSubheading
      {Microsoft - Compute Insights Team}{Redmond, Washington}
      {Software Engineer}{March 2014 - September 2015}
      \resumeItemListStart
      \resumeItem{Built tools to manage and observe Data Science jobs}
      \resumeItem{Built data visualization tools based on insights from low-level hardware metrics}
      \resumeItem{Wrote introductory courses on OSS Big Data concepts, notebooks and Hadoop for my team}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Scala, F\#, C\#, Hadoop, HDInsight, D3.js}\\

    %   \resumeTech{Theory}{Artificial intelligence, Data science and Data mining.}

    \resumeSubHeadingListEnd
% ---

% PROGRAMMING SKILLS
\section{Technical skills}
  \resumeSubHeadingListStart
  
  \resumeSubItem{\textbf{Programming languages:} Python, SQL, Java, Scala, Rust, F\#/.NET, JavaScript/Node}
  
  \resumeSubItem{\textbf{Cloud services:} Azure, GCP}
  
  \resumeSubItem{\textbf{Scripting/Infrastructure:} Terraform, Docker, Kubernetes, Bash, Powershell, Bicep}
  
  \resumeSubHeadingListEnd

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carleton University}{Ottawa, Ontario, Canada}
      {B.Sc in Computer Science}{September 2009 - February 2014}
      \resumeItemListStart
      \resumeItem{Served as head of Services for the Computer Science Society}
      \resumeItem{Deployed OpenStack for students to try out cloud computing}
      \resumeItem{Worked as a software contractor part-time}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% ---



% ---
\end{document}
